### 2017-07-14 architecture.tex
Minor

\textbf{ReadAccess:} A set of policies that define who can
access data, under what conditions, and

>>>>

\textbf{ReadAccess:} A set of policies that define who can
access data, under what conditions, and for what period of time. 
Policies can define individual users or groups of users, particular
authentication requirements (e.g., using two factor authentication), 
and for arbitrary periods of time from days to years.

\textbf{ExportControl:} Specifies if derived or copied data
can be exported outside of the safe collection.

\textbf{LinkControl:} An advanced policy that permits
or prohibits datasets within a safe collection being
combined. This is an important control as some datasets
are intentionally split and linking restricted for purposes
of deidentification or anonymization .
